An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-19 main.tex
addressing vince's comments

\begin{abstract}
    We present insights and empirical results from an extensive numerical
    study of the evolutionary dynamics of the iterated prisoner's dilemma.
    Fixation probabilities for Moran processes are obtained
    for all pairs of 164 different strategies including classics such as TitForTat, zero
    determinant strategies, and many more sophisticated strategies.
    Players with long memories and sophisticated behaviours outperform
    many strategies that perform well in a two player setting. Moreover we
    introduce several strategies trained with evolutionary algorithms to
    excel at the Moran process. These strategies are excellent invaders
    and resistors of invasion and in some cases naturally evolve handshaking
    mechanisms to resist invasion. The best invaders were those trained
    to maximize total payoff while the best resistors invoke handshake mechanism.
    This suggests that while maximizing individual payoff
    can lead to the evolution of cooperation through invasion, the relatively
    weak invasion resistance of payoff maximizing strategies are not as
    evolutionarily stable as strategies employing handshake mechanisms.
\end{abstract}

@@

To complement Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
and~\ref{fig:ranks_v_size_coexist} show
the rank of each strategy based on \(x_{N/2}\).
Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
and~\ref{tbl:ranks_v_size_coexist} show the same information for a selection of
strategies:

>>>>

\begin{abstract}
    We present insights and empirical results from an extensive numerical
    study of the evolutionary dynamics of the iterated prisoner's dilemma.
    Fixation probabilities for Moran processes are obtained
    for all pairs of 164 different strategies including classics such as TitForTat, zero
    determinant strategies, and many more sophisticated strategies.
    Players with long memories and sophisticated behaviours outperform
    many strategies that perform well in a two player setting. Moreover we
    introduce several strategies trained with evolutionary algorithms to
    excel at the Moran process. These strategies are excellent invaders
    and resistors of invasion and in some cases naturally evolve handshaking
    mechanisms to resist invasion. The best invaders were those trained
    to maximize total payoff while the best resistors invoke handshake mechanisms.
    This suggests that while maximizing individual payoff
    can lead to the evolution of cooperation through invasion, the relatively
    weak invasion resistance of payoff maximizing strategies are not as
    evolutionarily stable as strategies employing handshake mechanisms.
\end{abstract}

@@

To complement Figures~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist}, \ref{fig:ranks_v_size_coexist} shows
the rank of each strategy based on \(x_{N/2}\).
Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
and~\ref{tbl:ranks_v_size_coexist} show the same information for a selection of
strategies:
